\documentclass[../veristore_security_model.tex]{subfiles}

\begin{document}
\section{Threat Analysis: STRIDE}

% COMMENT: This section applies the STRIDE framework to systematically identify threats. For each
% STRIDE category, list potential threats discovered during brainstorming. Express threats as
% "Entity X performs action Y resulting in negative outcome Z". Don't worry about mitigations yet;
% just document all potential threats. Each threat will be resolved in the next section.

\subsection{Spoofing}

% COMMENT: Threats where attackers pretend to be someone or something else. Examples: impersonating
% legitimate clients, forging server identities, replaying old authentication tokens, masquerading
% as storage servers to receive fragments. Consider both client-to-server and server-to-server
% authentication.

\subsubsection{S.1: Client Impersonation}

% THREAT: An attacker impersonates a legitimate client and stores malicious data or retrieves
% other users' data.

\subsubsection{S.2: Server Impersonation}

% THREAT: An attacker impersonates a storage server and receives fragments from clients, potentially
% learning information about stored data.

\subsubsection{S.3: Fingerprint Source Forgery}

% THREAT: An attacker forges the source of fingerprints during cross-checksum verification,
% causing servers to trust malicious fingerprint values.

\subsection{Tampering}

% COMMENT: Threats where attackers modify data in transit or at rest. Examples: corrupting
% fragments in storage, modifying fragments in transit, tampering with fingerprints, altering
% encoded data before distribution. Consider both accidental corruption and malicious modification.

\subsubsection{T.1: Fragment Corruption in Storage}

% THREAT: A malicious or compromised storage server modifies fragments at rest, causing data
% corruption that will be detected only upon retrieval.

\subsubsection{T.2: Fragment Modification in Transit}

% THREAT: A network attacker intercepts and modifies fragments or fingerprints during transmission
% between client and servers or between servers.

\subsubsection{T.3: Fingerprint Tampering}

% THREAT: An attacker modifies fingerprints to match corrupted fragments, bypassing integrity
% verification.

\subsubsection{T.4: Erasure Code Parameter Manipulation}

% THREAT: An attacker manipulates encoding parameters (m, n, or field size) causing incorrect
% encoding that appears valid but cannot be decoded.

\subsection{Repudiation}

% COMMENT: Threats where attackers perform actions that cannot be traced back to them. Examples:
% storing data without audit trail, deleting fragments without logging, modifying data with no
% accountability. This may be less critical for an academic prototype but should be considered
% for production systems.

\subsubsection{R.1: Anonymous Data Storage}

An unauthenticated actor can submit arbitrary blocks without a durable identity binding.
If abuse occurs (for example, storing prohibited content or intentionally filling capacity),
operators cannot reliably attribute actions to a specific principal, weakening accountability
and incident response.

\subsubsection{R.2: Fragment Deletion Without Logging}

A compromised or misconfigured storage server can delete local fragments and return standard
HTTP error responses later, while leaving little or no tamper-evident audit trail. In that
case, the system can observe data loss but cannot prove which server performed the deletion
or when the deletion occurred.

\subsubsection{R.3: Untrackable Verification Failures}

When the client receives inconsistent fragment responses, weak request correlation and
insufficiently structured logs can make it difficult to attribute corruption to a specific
server instance over time. This enables a Byzantine server to intermittently misbehave while
plausibly denying responsibility.

\subsection{Information Disclosure}

% COMMENT: Threats where attackers steal or learn sensitive information. Examples: reading
% fragments from storage, inferring data patterns from fingerprints, eavesdropping on network
% traffic, exploiting verbose error messages. Consider whether data confidentiality is in scope
% or if encryption is assumed to be handled separately.

\subsubsection{I.1: Fragment Eavesdropping}

An on-path attacker observing client-to-server traffic can capture fragment payloads in transit.
If the attacker collects at least $m$ fragments for the same block, they can reconstruct the
original plaintext object because erasure coding provides redundancy, not confidentiality.

\subsubsection{I.2: Storage Server Data Access}

A storage server operator (or a host compromise) can read fragment files at rest directly from
disk. Although one server typically holds only one fragment per block, repeated observation
across many blocks still discloses user data patterns and potentially sensitive content.

\subsubsection{I.3: Fingerprint Analysis}

An attacker who collects cross-checksum material (hashes, fingerprints, and metadata) can run
offline analysis to correlate uploads, infer duplicate content patterns, or support dictionary
style guessing against predictable objects. While fingerprints are not raw data, metadata leakage
still increases attacker knowledge about stored content.

\subsubsection{I.4: Error Message Information Leakage}

Verbose API errors and debug logs may expose internal identifiers, verification outcomes,
fragment indices, and topology details (server IDs and ports). This information can be used by
attackers to target specific nodes, optimize denial-of-service behavior, or refine tampering
attempts.

\subsection{Denial of Service}

% COMMENT: Threats where attackers disrupt legitimate system operation. Examples: exhausting
% storage capacity, flooding network with requests, corrupting fragments to make data unrecoverable,
% causing expensive cryptographic operations. Consider both resource exhaustion and functional
% denial of service.

\subsubsection{D.1: Storage Exhaustion}

% THREAT: An attacker stores excessive data, filling storage servers and preventing legitimate
% users from storing data.

\subsubsection{D.2: Fragment Unavailability}

% THREAT: An attacker compromises more than n-m servers or corrupts more than n-m fragments,
% making data unrecoverable.

\subsubsection{D.3: Verification Flooding}

% THREAT: An attacker triggers excessive verification operations, consuming CPU resources with
% expensive finite field arithmetic and cryptographic operations.

\subsubsection{D.4: Network Bandwidth Exhaustion}

% THREAT: An attacker floods the network with fragment requests or verification messages,
% preventing legitimate communication.

\subsection{Elevation of Privilege}

% COMMENT: Threats where attackers gain capabilities they are not authorized to have. Examples:
% exploiting buffer overflows to execute arbitrary code, bypassing access controls, escalating
% from client to server privileges. Consider both implementation vulnerabilities and design flaws.

\subsubsection{E.1: Code Injection via Malformed Input}

% THREAT: An attacker sends maliciously crafted fragments or fingerprints that exploit parsing
% vulnerabilities, leading to arbitrary code execution on servers.

\subsubsection{E.2: Verification Bypass}

% THREAT: An attacker discovers a way to bypass fingerprint verification, allowing corrupted
% fragments to be accepted as valid.

\subsubsection{E.3: Cryptographic Parameter Override}

% THREAT: An attacker manipulates system parameters (fingerprint size, field size, collision
% probability) to weaken security and enable attacks.

\subsubsection{E.4: Server-to-Server Privilege Escalation}

% THREAT: A compromised storage server exploits inter-server protocols to gain control over
% other servers or access fragments it should not have.

\newpage
\end{document}