\documentclass[../veristore_security_model.tex]{subfiles}

\begin{document}
\section{Document Maintenance}

% COMMENT: Establish procedures for keeping this security model up-to-date. Specify when the
% document should be reviewed and updated: after major design changes, when new components are
% added, at project milestones, before releases. Assign responsibility for maintaining the document.

\subsection{Review Schedule}

Security model reviews follow a predictable schedule tied to engineering milestones:
\begin{itemize}
    \item Weekly during active development (Sunday code review window).
    \item At the end of each project week before TODO ownership is updated.
    \item Before demos or external presentations where security claims are shown.
    \item Immediately after changes to security-critical code paths, including:
    \begin{itemize}
        \item \texttt{src/network/server.py} request validation and verification handling.
        \item \texttt{src/network/client.py} retrieval verification and quorum behavior.
        \item \texttt{src/verification/verifier.py} consistency checks and decision logic.
    \end{itemize}
\end{itemize}

Albert owns the maintenance schedule for backend-owned sections, Mac owns the same process for security-owned sections, and Section 14 status is confirmed jointly during weekly sync.

\subsection{Change Process}

All updates to this document use the same workflow as code changes:
\begin{enumerate}
    \item Identify trigger: a new threat, mitigation change, dependency update, or behavior change in implementation.
    \item Update the relevant section in \texttt{docs/Security Model/sections/} with concrete impact and file/function references when available.
    \item Run peer review with the section owner pair (Albert/Mac) during the next scheduled review, or immediately for high-risk changes.
    \item Merge the documentation update in the same PR as the code change when possible; otherwise link the follow-up documentation PR in the code PR notes.
    \item Record the update in Section 14.3 (Version History) with date and summary.
\end{enumerate}

If an implementation change affects a documented mitigation but the document is not updated in the same cycle, the change is considered incomplete until the security model is synchronized.

\subsection{Version History}

\begin{itemize}
    \item \textbf{Version 0.1} (February 16, 2026): Initial draft - high-level security model with component stubs
    \item \textbf{Version 0.1.001} (February 16, 2026):
    \begin{itemize}
        \item Added descriptions of external libraries
        \item Added Administrator trust level and example administrators
    \end{itemize}
    \item \textbf{Version 0.1.002} (March 1, 2026):
    \begin{itemize}
        \item Split \texttt{.tex} file into sections for easier maintenance.
        \item Changes to preamble re: formatting and spacing.
    \end{itemize}
    \item \textbf{Version 0.1.1} (March 15, 2026):
    \begin{itemize}
        \item Completed sections 1.1 and 1.2.
        \item Inserted a \textbackslash\texttt{newpage} control at the end of each section document.
        \item Completed section 3
        \item Completed section 6.2 \& 6.4
        \item Updated and verified section 4.1
    \end{itemize}
    \item \textbf{Version 0.1.2} (March 28, 2026):
    \begin{itemize}
        \item Completed Section 8, ``Protected Assets''
    \end{itemize}
    \item \textbf{Version 0.2.0} (April 4, 2026):
    \begin{itemize}
        \item Added Section 10 intro, ``Security Guarantees Achieved''
        \item Added Section 10.1, ``Spoofing''
        \item Added Section 10.2, ``Tampering''
    \end{itemize}
\end{itemize}

\newpage
\end{document}
