\documentclass[../veristore_security_model.tex]{subfiles}

\begin{document}
\section{Threat Resolutions}

% COMMENT: For each threat identified in the previous section, document its resolution. Classify
% each threat as: (1) already mitigated by current design, (2) mitigated by dependency,
% (3) requires mitigation, (4) dependency's responsibility, or (5) accepted risk. For mitigated
% threats, describe the mitigation and assign testing to verify it. For unmitigated threats
% requiring action, assign an owner and track to completion.

\subsection{Spoofing Threat Resolutions}

\subsubsection{S.1: Client Impersonation}
\begin{itemize}
    \item \textbf{Status}: Requires mitigation for multi-user deployment. Partially mitigated by current design.
    \item \textbf{Resolution}: The current implementation requires a bearer token on all \texttt{PUT}, \texttt{GET}, and \texttt{DELETE} endpoints, which blocks unauthenticated clients from impersonating a legitimate caller. The FastAPI server refuses to start without a configured \texttt{VERI\_STORE\_TOKEN} and each route verifies the supplied bearer token before any fragment operation is performed.
    
    For the current single-client implementation, this token is shared across the deployment rather than bound to an individual user identity, so any party that learns the token can still act as the client and access any known block identifier. A production deployment would therefore need to extend this design with per-user authentication and authorization and enforcing ownership checks on endpoint calls.
    \item \textbf{Owner}: Mac
    \item \textbf{Testing}: Integration tests should verify that \texttt{PUT}, \texttt{GET}, and \texttt{DELETE} requests with an invalid or missing bearer token return \texttt{HTTP 401}, while the \texttt{/health} endpoint remains publicly accessible. Configuration tests should verify that the server fails to initialize when \texttt{VERI\_STORE\_TOKEN} is not set.
    
    For a future multiple-user implementation, authorization tests should be added to confirm that one authenticated user cannot retrieve, overwrite, or delete a fragment belonging to a different authenticated user.
\end{itemize}

\subsubsection{S.2: Server Impersonation}
\begin{itemize}
    \item \textbf{Status}: Accepted risk for current implementation. Would require mitigation for any networked production deployment.
    \item \textbf{Resolution}: In the current implementation, the client communicates with the servers over HTTP in the clear using configured host and port values and does not verify a server certificate, pinned key, or other server identity credentials before sending or accepting fragment data. As a result, bearer token authentication protects the server from unauthenticated clients, but it does not protect the client from sending fragments to an adversarial endpoint that successfully impersonate a storage server.
    
    This is considered an acceptable risk in this prototype since the deployment is limited to trusted \texttt{localhost} processes on a single machine. For any non-local or multi-host deployment, however, Veri-Store should run behind TLS with certificate validation and infrastructure-level server authentication, so that the client can confirm it is communicating with the intended storage node before transmitting fragment data or trusting retrieval responses.
    \item \textbf{Owner}: Mac
    \item \textbf{Testing}: For this prototype, manually verify that only \texttt{localhost} endpoints are targeted and does not claim transport security beyond that environment.
    
    For a production deployment, integration tests should confirm that the client rejects connections with invalid, expired, or mismatched server certificates, and accepts connections only when the certificate chain and expected server identity are successfully validated.
\end{itemize}

\subsubsection{S.3: Fingerprint Source Forgery}
\begin{itemize}
    \item \textbf{Status}: Requires mitigation
    \item \textbf{Resolution}: During retrieval, the client currently trusts the first successful \texttt{fpcc\_json} it receives and uses it as the reference value for subsequent fragment verification. This means the client verifies the fragment consistency against a server-supplied \texttt{fpcc}, not against a separately trusted record. A byzantine server, or a set of colluding byzantine servers, can therefore construct a forged \texttt{fpcc} that is internally consistent with corrupted fragments. If at least $m$ servers return the same forged \texttt{fpcc}, the client may accept those fragments and reconstruct corrupted data without detecting the deception.
    
    The mitigation is to establish an authenticated source of truth for the \texttt{fpcc}. For example, the client should persist the original \texttt{fpcc} produced at \texttt{PUT} time and compare all retrieved fragments against the retained value, or the system should store a signed MAC-protected \texttt{fpcc} in a trusted metadata service.
    
    Cross-server agreement alone is not sufficient, because multiple malicious servers can agree on the same forged metadata.
    \item \textbf{Owner}: Mac
    \item \textbf{Testing}: Add retrieval tests in which one server returns a forged \texttt{fpcc} and corrupted fragment, confirming the client rejects it when compared against a trusted stored \texttt{fpcc}. Add a stronger adversarial test in which $m$ colluding servers return the same forged \texttt{fpcc} and mutually consistent corrupted fragments and verify that retrieval still fails once the client uses the trusted original \texttt{fpcc} rather than a server-supplied one. Regression tests should also verify that honest retrieval still succeeds when all servers return the correct \texttt{fpcc}.
\end{itemize}

\subsection{Tampering Threat Resolutions}

\subsubsection{T.1: Fragment Corruption in Storage}
\begin{itemize}
    \item \textbf{Status}: Mitigated in current implementation
    \item \textbf{Resolution}: Veri-Store detects byte-level corruption of stored fragments during verification and retrieval. Each fragment is checked against the stored \texttt{fpcc} using a \texttt{SHA-256} hash check, and for indices $i < m$, an additional homomorphic fingerprint check.
    
    A storage server can still alter bytes on disk, but the modified fragment will not verify against the original \texttt{fpcc} and will therefore be rejected before reconstruction. In the current 3-of-5 deployment, the system can tolerate such tampering as long as at least $m = 3$ honest fragments remain available.
    \item \textbf{Owner}: Mac
    \item \textbf{Testing}: Use the existing verifier and client retrieval tests that inject corrupted fragment bytes and confirm that verification returns \texttt{HASH\_MISMATCH} or otherwise rejects the tampered fragment. 
    
    End-to-end tests should also confirm that retrieval succeeds when fewer than $n - m = 2$ fragments are corrupted and fails cleanly when too many fragments are corrupted.
\end{itemize}

\subsubsection{T.2: Fragment Modification in Transit}
\begin{itemize}
    \item \textbf{Status}: Partially mitigated in current implementation
    \item \textbf{Resolution}: If an attacker modifies fragment bytes while they are in transit, the modified payload will usually be detected by the \texttt{fpcc}-based verification used for storage integrity, described in section T.1. The receiving server checks uploaded fragments during \texttt{PUT}, and the client re-verifies fragments during \texttt{GET} before reconstruction.
    
    As a result, byte-level tampering of fragment payloads does not normally succeed silently. However, this mitigation applies only when the fragment is checked against a trusted \texttt{fpcc}. If the attacker can also tamper with the \texttt{fpcc} or impersonate a server, the attack becomes part of the threats described in sections T.3 or S.2 rather than a simple fragment-byte modification. For that reason, in a production deployment, transport hardening such as TLS is recommended.
    \item \textbf{Owner}: Mac
    \item \textbf{Testing}: Verify that tampering with fragment bytes in \texttt{PUT} requests causes the server to reject the fragment with \texttt{HTTP 422}, and that tampering with bytes in \texttt{GET} responses causes the client to discard the fragments during retrieval. For deployment hardening, add integration tests confirming that transport protections prevent or survive in-transit modification attempts.
\end{itemize}

\subsubsection{T.3: Fingerprint Tampering}
\begin{itemize}
    \item \textbf{Status}: Requires mitigation
    \item \textbf{Resolution}: The current verification logic proves that a fragment is consistent with the \texttt{fpcc} supplied to the checker, but it does not independently authenticate the source of that \texttt{fpcc}. An attacker who can alter both fragment data and the associated \texttt{fpcc} can construct a forged pair that remains internally consistent. During retrieval, the client currently adopts the first successful \texttt{fpcc} it receives as the reference value, so a malicious server or colluding set of servers can potentially cause corrupted fragments to be accepted if they all present the same forged \texttt{fpcc}. 
    
    This can be mitigated by binding retrieval to a trusted \texttt{fpcc}, such as by storing the original client-generated \texttt{fpcc} locally, retrieving it from a trusted metadata service, or authenticating it with a digital signature or MAC. Cross-server agreement alone is not sufficient, because multiple malicious servers can agree on the same forged metadata.

    See also section S.3.
    \item \textbf{Owner}: Mac
    \item \textbf{Testing}: Add tests in which a server returns a forged \texttt{fpcc} together with tampered fragment data, and confirm that the client rejects the response when compared against a trusted stored \texttt{fpcc}. A stronger test will consist of $m$ colluding malicious servers that all return the same forged \texttt{fpcc} \textendash{} retrieval should still fail once the client verifies against the trusted original \texttt{fpcc} rather than a server-supplied one.
\end{itemize}

\subsubsection{T.4: Erasure Code Parameter Manipulation}
\begin{itemize}
    \item \textbf{Status}: Partially mitigated, but requires additional mitigation
    \item \textbf{Resolution}: The current implementation already validates some coding-parameter tampering, but not all of it. On \texttt{PUT}, malformed requests with impossible parameters such as \texttt{threshold\_m > total\_n} are rejected by request validation, and duplicate writes with conflicting metadata are rejected with \texttt{HTTP 409}. During decode, the client also checks that all accepted fragments agree on \texttt{block\_id}, \texttt{total\_n}, and \texttt{threshold\_m}. These controls limit straightforward manipulation of coding parameters. 
    
    However, the decoder currently takes \texttt{original\_length} from the first accepted fragment and does not cross-check it against the other verified fragments. As a result, a malicious server whose response is accepted first can potentially cause silent truncation or padding effects in the reconstructed output. 
    
    The mitigation is to authenticate all reconstruction metadata as part of a trusted object manifest or bind it cryptographically to the trusted \texttt{fpcc}, and to require the client to confirm that all accepted fragments agree on \texttt{original\_length} before decoding.
    \item \textbf{Owner}: Mac
    \item \textbf{Testing}: The existing validation tests reject impossible \texttt{PUT} requests (e.g., \texttt{threshold\_m > total\_n}). 
    
    Add retrieval tests where one fragment reports manipulated \texttt{total\_n}, \texttt{threshold\_m}, and/or \newline \texttt{original\_length}. The client should fail closed on metadata disagreement, and after the mitigation is implemented, tests should verify that a forged \texttt{original\_length} can no longer silently truncate or extend reconstructed output.
\end{itemize}

\subsection{Repudiation Threat Resolutions}

\subsubsection{R.1: Anonymous Data Storage}
\begin{itemize}
\item \textbf{Status}: Accepted risk for academic prototype
\item \textbf{Resolution}: The current implementation does not enforce authentication for HTTP endpoints, prioritizing simplicity for the course project scope. Production deployments would add an authentication layer (token-based or certificate-based) at the reverse proxy or API gateway to bind actions to authenticated principals. For the controlled laboratory environment, anonymous access is acceptable.
\item \textbf{Owner}: Albert
\item \textbf{Testing}: Manual verification that endpoints accept requests without authentication headers. For production systems, integration tests should verify that unauthenticated requests are rejected with HTTP 401 when authentication is enabled.
\end{itemize}

\subsubsection{R.2: Fragment Deletion Without Logging}
\begin{itemize}
\item \textbf{Status}: Already mitigated by request logging implementation
\item \textbf{Resolution}: The FastAPI middleware logs all HTTP requests including DELETE operations in \texttt{src/network/server.py}, providing an audit trail with timestamps, server identity, fragment identifiers, and outcomes. Logs are written to standard output and can be aggregated to centralized log management systems for long-term retention.
\item \textbf{Owner}: Albert
\item \textbf{Testing}: Perform DELETE requests and verify that log messages appear for each operation with correct block\_id, index, and status code. Test suite should capture log output and assert that deletion events are properly recorded.
\end{itemize}

\subsubsection{R.3: Untrackable Verification Failures}
\begin{itemize}
\item \textbf{Status}: Already mitigated by verification failure logging
\item \textbf{Resolution}: When fragment verification fails during PUT operations, the server logs detailed context at WARNING level in \texttt{src/network/server.py}, recording server ID, block ID, fragment index, and the specific check that failed. This structured logging enables operators to correlate failures over time and attribute Byzantine behavior by analyzing aggregated logs for patterns of repeated failures from specific server instances.
\item \textbf{Owner}: Albert
\item \textbf{Testing}: Inject corrupted fragments during PUT operations and verify that WARNING level log entries appear with full context. Test multiple corrupted requests and verify that log analysis can identify patterns of failures from a specific server.
\end{itemize}

\subsection{Information Disclosure Threat Resolutions}

\subsubsection{I.1: Fragment Eavesdropping}
\begin{itemize}
\item \textbf{Status}: Dependency responsibility
\item \textbf{Resolution}: Transport layer confidentiality is outside the scope of veri-store's erasure coding and integrity verification design. In production deployments, operators must terminate TLS at the edge (reverse proxy, load balancer, or API gateway) to provide transport encryption. The erasure coding scheme provides no inherent confidentiality; applications requiring confidentiality must encrypt data at the application layer before erasure encoding or rely on TLS for transport security.
\item \textbf{Owner}: Albert (deployment/documentation)
\item \textbf{Testing}: Verify that production deployments use HTTPS endpoints. Network traffic capture tools should confirm that fragment payloads are encrypted in transit. For the academic prototype, document the assumption that HTTP is acceptable in controlled laboratory networks.
\end{itemize}

\subsubsection{I.2: Storage Server Data Access}
\begin{itemize}
\item \textbf{Status}: Accepted risk with operational controls
\item \textbf{Resolution}: Storage servers have direct filesystem access to fragment data at rest in the \newline \texttt{data/server\_N} directories. A single compromised server can read its local fragments but cannot reconstruct complete objects without collecting at least m fragments from other servers. In production, operators should use standard operating system access controls to restrict filesystem access to the server process user account. For stronger confidentiality, applications can encrypt data before submitting it to veri-store, treating the storage system as untrusted infrastructure.
\item \textbf{Owner}: Albert
\item \textbf{Testing}: Review filesystem permissions on fragment storage directories. Verify that only the server process owner can read fragment files. For encrypted deployments, verify that stored fragments contain ciphertext rather than plaintext by examining on-disk data.
\end{itemize}

\subsubsection{I.3: Fingerprint Analysis}
\begin{itemize}
\item \textbf{Status}: Partially mitigated by cryptographic hash collision resistance
\item \textbf{Resolution}: The fingerprinted cross-checksum includes SHA-256 hashes of all fragments and homomorphic fingerprints for the first m fragments. While these values do not directly expose plaintext content, they enable offline correlation attacks where an attacker can identify duplicate uploads by matching hash sets. The SHA-256 hash function provides preimage resistance, making dictionary attacks computationally expensive but not impossible for low-entropy data. Production systems requiring stronger privacy guarantees should encrypt objects before dispersal or add randomness to block identifiers to decorrelate metadata across uploads.
\item \textbf{Owner}: Albert
\item \textbf{Testing}: Store the same object multiple times and verify that fpcc values are deterministic. Attempt to correlate uploads by comparing stored fpcc\_json values. For systems requiring privacy, verify that client-side encryption is applied before erasure encoding.
\end{itemize}

\subsubsection{I.4: Error Message Information Leakage}
\begin{itemize}
\item \textbf{Status}: Already mitigated by structured error responses and controlled logging
\item \textbf{Resolution}: HTTP error responses return minimal context to clients via FastAPI's HTTPException mechanism in \texttt{src/network/server.py}, including only block ID, fragment index, and generic status descriptions without disclosing internal server topology or storage paths. Detailed diagnostic information such as verification failure details, stack traces, and internal state is written to server-side logs rather than returned to clients. The logging implementation records comprehensive context for operator debugging while preventing information disclosure to potentially hostile clients.
\item \textbf{Owner}: Albert
\item \textbf{Testing}: Trigger error conditions (404 not found, 409 conflict, 422 validation failure) and verify that HTTP responses contain only generic error messages without internal details. Verify that detailed diagnostic information appears in server logs but not in client responses. Test that stack traces and filesystem paths are not leaked in production error responses.
\end{itemize}

\subsection{Denial of Service Threat Resolutions}

\subsubsection{D.1: Storage Exhaustion}
\begin{itemize}
\item \textbf{Status}: %
\item \textbf{Resolution}: %
\item \textbf{Owner}: %
\item \textbf{Testing}: %
\end{itemize}

\subsubsection{D.2: Fragment Unavailability}
\begin{itemize}
\item \textbf{Status}: %
\item \textbf{Resolution}: %
\item \textbf{Owner}: %
\item \textbf{Testing}: %
\end{itemize}

\subsubsection{D.3: Verification Flooding}
\begin{itemize}
\item \textbf{Status}: %
\item \textbf{Resolution}: %
\item \textbf{Owner}: %
\item \textbf{Testing}: %
\end{itemize}

\subsubsection{D.4: Network Bandwidth Exhaustion}
\begin{itemize}
\item \textbf{Status}: %
\item \textbf{Resolution}: %
\item \textbf{Owner}: %
\item \textbf{Testing}: %
\end{itemize}

\subsection{Elevation of Privilege Threat Resolutions}

\subsubsection{E.1: Code Injection via Malformed Input}
\begin{itemize}
\item \textbf{Status}: %
\item \textbf{Resolution}: %
\item \textbf{Owner}: %
\item \textbf{Testing}: %
\end{itemize}

\subsubsection{E.2: Verification Bypass}
\begin{itemize}
\item \textbf{Status}: %
\item \textbf{Resolution}: %
\item \textbf{Owner}: %
\item \textbf{Testing}: %
\end{itemize}

\subsubsection{E.3: Cryptographic Parameter Override}
\begin{itemize}
\item \textbf{Status}: %
\item \textbf{Resolution}: %
\item \textbf{Owner}: %
\item \textbf{Testing}: %
\end{itemize}

\subsubsection{E.4: Server-to-Server Privilege Escalation}
\begin{itemize}
\item \textbf{Status}: %
\item \textbf{Resolution}: %
\item \textbf{Owner}: %
\item \textbf{Testing}: %
\end{itemize}

\newpage
\end{document}