\documentclass[../veristore_security_model.tex]{subfiles}

\begin{document}
\section{Data Flow Diagram}

% COMMENT: This section contains the graphical representation of data flows through veri-store.
% The DFD shows all major components, entry points, data stores, and how information moves
% between them. Use different colors for trust levels: green for trusted processes, red for
% untrusted entities/data, orange for semi-trusted. Number all data flows sequentially and label
% them with concise descriptions.

\begin{figure}[ht!]
\centering
\begin{tikzpicture}[node distance=2.5cm]

% External entities
\node (client) [entity, fill=trusted!30] {Client};
\node (network) [entity, fill=untrusted!30, right of=client, xshift=3cm] {Network};
\node (storage) [datastore, fill=semitrusted!30, below of=network, yshift=-1cm] {Fragment \newline Storage};

% Processes (all trusted - our code)
\node (encode) [process, below of=client, yshift=-0.5cm] {Encode \newline Block};
\node (fingerprint) [process, right of=encode, xshift=2cm] {Compute \newline Fingerprint};
\node (distribute) [process, below of=fingerprint, yshift=-0.5cm] {Distribute \newline Fragments};
\node (verify) [process, below of=distribute, yshift=-0.5cm] {Verify \newline Fragments};
\node (reconstruct) [process, left of=verify, xshift=-2cm] {Reconstruct \newline Block};

% Data flows
\draw [arrow] (client) -- node[anchor=east] {1. Data block} (encode);
\draw [arrow] (encode) -- node[anchor=south] {2. Fragments} (fingerprint);
\draw [arrow] (fingerprint) -- node[anchor=west] {3. Fingerprints} (distribute);
\draw [arrow] (distribute) -- node[anchor=west] {4. Fragment + \newline fingerprint} (network);
\draw [arrow] (network) -- node[anchor=west] {5. Store} (storage);
\draw [arrow] (storage) -- node[anchor=east] {6. Retrieve} (verify);
\draw [arrow] (verify) -- node[anchor=south] {7. Verified \newline fragments} (reconstruct);
\draw [arrow] (reconstruct) -- node[anchor=east] {8. Reconstructed \newline block} (client);

% Cross-checksum verification (dotted line to show verification flow)
\draw [arrow, dashed] (storage) to[bend left=30] node[anchor=west] {9. Cross-check \newline fingerprints} (verify);

\end{tikzpicture}
\caption{High-level data flow diagram for veri-store store and retrieve operations.}
\label{fig:dfd}
\end{figure}

\subsection{DFD Component Descriptions}

% COMMENT: Provide brief descriptions of each component in the DFD. Explain what each process
% does, what trust level it operates at, and what security properties it maintains. Describe
% external entities and data stores. Note any assumptions about data flows (e.g., authenticated
% channels, encrypted storage).

\subsubsection{Client}

The Client is the entry-point process that initiates store (PUT) and retrieve (GET) operations.
It is trusted to run the veri-store protocol correctly, but it is still treated as a software
component that can fail due to bugs or operator error. For writes, the Client invokes encoding,
computes the fingerprinted cross-checksum (fpcc), and dispatches fragments to storage servers.
For reads, it gathers candidate fragments, verifies them locally, and only then reconstructs the
original block. This placement makes the Client the final integrity decision point.

\subsubsection{Encode Block}

Encode Block is a trusted process that converts an input data block into $n$ Reed-Solomon
fragments with threshold $m$ (for this project, typically 3-of-5). The process pads input,
computes coded fragments, and tags each fragment with metadata (index, block id, $n$, $m$, and
original length). Its security role is correctness: if encoding is wrong, availability and
integrity both degrade because reconstruction may fail or produce incorrect bytes.

\subsubsection{Compute Fingerprint}

Compute Fingerprint is a trusted process that builds the fpcc structure used for integrity
verification. It computes per-fragment hash commitments and homomorphic fingerprints (for indices
below $m$), and derives challenge point $r$ via the random-oracle construction from fragment
hashes. The output fpcc binds fragments to a single logical block and enables later detection of
tampered, stale, or mismatched fragment responses.

\subsubsection{Distribute Fragments}

Distribute Fragments is a trusted client-side networking process that sends each fragment and the
shared fpcc to its designated server endpoint. It runs requests in parallel, applies timeout
bounds, and treats server failures as expected partial-fault behavior. The process succeeds only
if at least $m$ servers acknowledge storage, preserving the threshold availability assumption.

\subsubsection{Network}

Network is explicitly untrusted. An adversary may delay, drop, replay, reorder, or modify packets,
and may make individual servers appear unavailable. The design therefore does not rely on network
honesty for integrity: retrieved data is always re-verified against fpcc before decode. Timeouts
and best-effort fan-out/fan-in behavior are used so the client can tolerate partial outages.

\subsubsection{Fragment Storage}

Fragment Storage represents server-local persistent stores that hold fragment bytes and associated
metadata. It is semi-trusted for durability but not for integrity: servers can crash, lose state,
or return corrupted values. The threat model assumes these failures are detectable by client-side
verification and threshold reconstruction, rather than prevented by fully trusted storage nodes.

\subsubsection{Verify Fragments}

Verify Fragments is a trusted process that checks each retrieved fragment against fpcc before it is
eligible for decode. Verification first checks the fragment hash commitment and then (for indices
below $m$) checks the homomorphic fingerprint equation. Any fragment that fails consistency checks,
has malformed encoding, or disagrees on fpcc context is rejected. This step provides integrity
filtering under Byzantine or unreliable server behavior.

\subsubsection{Reconstruct Block}

Reconstruct Block is a trusted decoding process that rebuilds the original data from any $m$
verified fragments using Reed-Solomon decode. It runs only after the verification phase has
accepted enough fragments, then removes padding to recover the original byte length. Security-wise,
this enforces a strict pipeline: no unverified fragment is allowed to influence reconstructed
output.

\newpage
\end{document}
